---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mosdepth

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

An R package api to help run mosdepth and parse/visualise mosdepth output.

[**mosdepth**](https://github.com/brentp/mosdepth) is a commandline tool that quickly and efficiently calculates coverage from bam file inputs.

## Installation

You can install the development version of mosdepth from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("selkamand/mosdepth")
```

## Visualising mosdepth output

We start by loading the library

```{r example}
library(mosdepth)
```

Then we point towards the mosdepth output directory

```{r}
# Path to mosdepth output dir
mosdepth_dir = system.file("mosdepth_test_files", package="mosdepth")

# Create an object that keeps track of the output fils
mosdepth_output = mosdepth_collect_output_files(prefix = "E_coli", mosdepth_dir)

# Which output files do we have available? (not all options will produce the same set of files)
print(mosdepth_output)
```

Next we can run any `mosdepth_plot_`, `mosdepth_tabulate_`, or `mosdepth_calculate_` functions on this `mosdepth output` object. For example we could plot cumulative coverage distributions

```{r}
# Plot cumulative coverage distributions
mosdepth_plot_cumulative_coverage_distribution(mosdepth_output)
```

Or get a dataframe containing summary metrics

```{r}
# Get summary table
mosdepth_tabulate_summary(mosdepth_output)
```
